A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes

### 2015-10-22 imaging_demo/ms.tex
forgot to break up lines

Equation \ref{eqn:dirty-image-MOFF} is the optimal imaging equation used by the MOFF algorithm. While mathematically equivalent to Equation~\ref{eqn:dirty-image-FX}, squaring in image space rather than convolving in $uv$ space potentially saves orders of magnitude in computation.

>>>>

Equation \ref{eqn:dirty-image-MOFF} is the optimal imaging equation used by the 
MOFF algorithm. While mathematically equivalent to Equation~
\ref{eqn:dirty-image-FX}, squaring in image space rather than convolving in $uv$ 
space potentially saves orders of magnitude in computation.
